---
title       : Prediction Function for Iris Data
subtitle    : 
author      : Nate Reed
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

We used the Iris data set and built a predictive model. An accurate prediction of flower species was developed using only the following attributes:

- Sepal Length
- Sepal Width
- Petal Width
- Petal Length

--- .class #id 

## Plots

Shown here are plots relating pairs of sepal and petal attributes with species:

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(data=iris,  aes(x=Sepal.Length, y=Sepal.Width, color=Species, shape=Species)) + geom_point()
p2 <- ggplot(data=iris,  aes(x=Sepal.Length, y=Petal.Length, color=Species, shape=Species)) + geom_point()
p3 <- ggplot(data=iris,  aes(x=Sepal.Length, y=Petal.Width, color=Species, shape=Species)) + geom_point()
p4 <- ggplot(data=iris,  aes(x=Sepal.Width, y=Petal.Length, color=Species, shape=Species)) + geom_point()
p5 <- ggplot(data=iris,  aes(x=Sepal.Width, y=Petal.Width, color=Species, shape=Species)) + geom_point()
p6 <- ggplot(data=iris,  aes(x=Petal.Width, y=Petal.Length, color=Species, shape=Species)) + geom_point()

grid.arrange(p1, p2, p3, p4, p5, p6)
```

---

## Methodology

Random Forest, a highly accurate classification and regression algorithm, was used for the predictive model. The procedure was as follows:

1. Data was partitioned into training and test sets:
2. Random forest was applied to the training set to build the model. 
3. Random forest was applied to the test set to verify accuracy.

---

## Partitioning

```{r}
library(caret)
library(randomForest)
library(e1071)
data(iris)
set.seed(12345)
inTrain<-createDataPartition(iris$Species, p=0.7, list=FALSE)
training<-iris[inTrain,]
testing<-iris[-inTrain,]
```

---

## Modeling

First, the model was trained:

```{r}
modfit<-train(Species~., method="rf", data=training)
```

Model fit was assessed on the testing set. As we see below, there was only one inaccurate classification out of 45:

```{r}
predictions<-predict(modfit, testing[,-5])
table(predictions, testing$Species)
```

